Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-09-28 limits/ms.tex
New plots for sigma/beta comparison. New plots of recovered/true 2d mass distribution. Adjusted text.

The main results from modelling these different configurations are shown in black in
\figref{main results} and \figref{main results pixel-wise}. Each subplot corresponds to a different galaxy and
the vertical axis shows the range of `quality' of recovery. In \figref{main results}, this quality is
defined over radial bins of mass as
%
\begin{equation} \label{badness}
  f_r = \frac {\int \left|\Delta M(r)\right|\; dr } {\int M(r)\; dr}
\end{equation}
%
while in \figref{main results pixel-wise} the quality is defined over all the pixels
%
\begin{equation} \label{badness}
f_\theta = \frac
       {\int \left|\Delta M(\vec\theta)\right| \; d \vec{\theta} }
       {\int M(\vec\theta) \; d \vec\theta}
\end{equation}
In both cases, the delta difference is between a single recovered model and the known mock galaxy.
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

@@

@@

\item Add example plot of the projected density and recovered
  projected density (cf. plots Jonathan made for Justin's ERC
  proposal).

@@

\item Take a model that is well constrained by strong lensing
  (e.g. quad with time delays). Calculate $\sigma_p(R)$ for each model
  in the ensemble using the kinematics module. Compare this with the
  true $\sigma_p(R)$ from the mock data to obtain a $\chi^2$ (actually
  a $\chi^2$ this time!).  Show the true $\sigma_p(R)$ and overlay
  coloured bands from the lensing model ensemble assuming $\beta = 0$
  or $\beta = 1$.

>>>>

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ {\bf (Left)} Mock data distribution on coarse grid. {\bf (Right)} Recover ensemble average kappa distribution.}
\label{2d mass reconstruction}
\end{figure*}

%
\begin{equation} \label{badness}
  f_r = \frac {\int \left|\Delta M(r)\right|\; dr } {\int M(r)\; dr}
\end{equation}
%
while in \figref{main results pixel-wise} the quality is defined over all the pixels
%
\begin{equation} \label{badness}
f_\theta = \frac
       {\int \left|\Delta M(\vec\theta)\right| \; d \vec{\theta} }
       {\int M(\vec\theta) \; d \vec\theta}
\end{equation}
In both cases, the delta difference is between a single recovered model and the known mock galaxy.
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

@@

\begin{figure*}
\includegraphics[width=0.49\textwidth]{BCZContrastR1R3_TmS_sb.pdf}
\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sb.pdf}
\caption{ 
(Left) Projected radially averaged velocity dispersion for Sdom/DMcuspy ZConstrastR1R3 models and the mock data.
(Right) Projected radially averaged velocity dispersion for Sdom/DMcuspy QuadR1a models and the mock data.
}
\label{main results pixel-wise}
\end{figure*}

@@

\item \sout{Add example plot of the projected density and recovered
  projected density (cf. plots Jonathan made for Justin's ERC
proposal).}

@@

\item \sout{Take a model that is well constrained by strong lensing
  (e.g. quad with time delays). Calculate $\sigma_p(R)$ for each model
  in the ensemble using the kinematics module. Compare this with the
true $\sigma_p(R)$ from the mock data} to obtain a $\chi^2$ (actually
  a $\chi^2$ this time!).  \sout{Show the true $\sigma_p(R)$ and overlay
  coloured bands from the lensing model ensemble assuming $\beta = 0$
or $\beta = 1$.}
